%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://sourabhbajaj.com/}{\Large Dev manghat}} & Email: \href{mailto:mangha_d1@denison.edu}{sourabh@sourabhbajaj.com}\\
  \href{https://sourabhbajaj.com/}{sourabhbajaj.com} & Mobile: \href{tel:+11234567890}{+1-740-404-8653} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Denison University}{Columbus, OH}
      {Bachelor of Science in Computer Science; Bachelor of Art in Economics; GPA: 3.60}{Aug 2023 -- May 2027}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}{Python, C++, SQL, Javascript, HTML, CSS, R, Latex, Git}
    \resumeSubItem{Technologies}{GitHub, Android Studio, Pandas, NumPy, Regex, Microsoft Excel, Microsoft Word}
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Financial Literacy Website}
      {Generated over \$1,000 in referral earnings by designing and developing a website that educated users on the benefits of credit card usage and encouraged sign-ups through my referral link.}
    \resumeSubItem{Python Automation Scripts}
      {Designed and implemented a Python script to automate the calculation of monthly work hours and corresponding pay. Script executes daily to update and summarize work hours and payment details at month-end.}
    \resumeSubItem{Android Ap}
      {Designed and developed a fitness and health application for Android devices that uses SQL database to track progress.}
    \resumeSubItem{Password Game}
      {Built an interactive web game using JavaScript and HTML, challenging users with escalating regex-based password requirements to enhance problem-solving engagement.}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Community Advivor (RA)}{Granville, OH}
      {Residential Communities \& Housing}{May 2025 -- Present}
      \begin{itemize}
          \item Demonstrated leadership and leveraged organizational and problem-solving skills by mentoring peers and resolving conflicts.
          \item Created an inclusive and supportive environment for 25+ upperclassmen residents, addressing social and academic concerns while managing on-call responsibilities for more than 300 residents.
    \end{itemize}

\resumeSubheading
      {Research Assistant}{Granville, OH}
      {Mathematics Department}{January 2025 -- May 2025}
      \begin{itemize}
          \item Conducted research on Election Forecasting using BERT embeddings and Ridge Regression to model Congressional ideology, and applied entropy-based methods to quantify intra-party 
          \item Presented our research at the Indiana-Kentucky-Ohio MAA Tri-Section Meeting.
    \end{itemize}


%-----------RELEVENT COURSEWORK-----------------
\section{Relevant Coursework}
Data Structures • Applied Statistics • Linear Algebra • Discrete Mathematics • Multivariable Calculus

\end{document}
